Simulation for generic Cormotif model

### 2017-09-28 analysis/Simulation_generic_Cormotif.Rmd
show loglike

---
title: "Simulation for generic Cormotif model"
author: "First Last"
date: "9/24/2017"
output: html_document
---

@@

Then suppose we don't know $k$. Set $K = 1:6$ and apply BIC and AIC.

```{r,cache=TRUE}
fit2 = generic.cormotif(betahat,sebetahat,K=1:6,mess=FALSE)
```

@@

>>>>

---
title: "Simulation for generic Cormotif model"
author: "Zhiwei Ma"
date: "9/24/2017"
output: html_document
---

@@

Then suppose we don't know $k$. Set $K = 1:10$ and apply BIC and AIC.

```{r,cache=TRUE}
fit2 = generic.cormotif(betahat,sebetahat,K=1:10,mess=FALSE)
```

@@

The loglikelihood values:

```{r}
fit2$loglike
```
